Title of the document here

### 2015-02-06 rmtw/assignment_1/assignment_1.tex
Fixed merge conflict between versions

  Population: limited to the SEM program. (Count students if it's available somewhere).
  Cluster sampling / single stage - Not possible to get all the names of all possible respondents - Babbie 2007
  nonprobability sample - convenience sample - chosen on their availability and convenience. Not ideal, but best we can probably do considering its single stage etc (ideally we would do random sampling)
  stratification will not occur. Ideally we will have a good representation, but again, due to not having all the names and the convenience method, we cannot ensure that the population is stratisfied plus irrelevent
  total at SEM = ~300. (Count how many in the facebook groups, that's the sample size - Estimate how many will actually respond, how much error we can tolerate (\%4 probably - confidence interval) - Use the sample size method by fowler?

@@

The population of this survey is the students of the Software Engineering and Management programme (SEM) at Gothenburg University. The industry is left out of the population since they are more likely to have a lot of experience with certain languages which may cause them to be biased towards that language. The SEM program was chosen due to it being accessible for the researchers. 
\newline

TABLE HERE
Variable : RQ : Item on Survey

@@

Non responses are another issue we will likely face. *** add more?

@@

\SubSection{Threats to Validity}
Bias in languages and experience

  Validity threats:
    Willingness to participate - There is no incentive other than that they might have to do this next year
    The results could be meaningless
    How we will handle response bias:
      Non responses, how we handle them
  Potential errors - sampling errors and biases

  Sampling bias is a considerable challenge in research \cite{easterbrook2008selecting}

>>>>

  Population: limited to the SEM program. (Count students if it's available somewhere).
  Cluster sampling / single stage - Not possible to get all the names of all possible respondents - Babbie 2007
  nonprobability sample - convenience sample - chosen on their availability and convenience. Not ideal, but best we can probably do considering its single stage etc (ideally we would do random sampling)
  stratification will not be enforced. Ideally we will have 1/3,1/3,1/3 but we cannot enfore. The groups are open and public
  total at SEM = ~300. (Count how many in the facebook groups, that's the sample size - Estimate how many will actually respond, how much error we can tolerate (\%4 probably - confidence interval) - Use the sample size method by fowler?

@@

The population of this survey is the students of the Software Engineering and Management programme (SEM) at Gothenburg University. The industry is left out of the population since they are more likely to have a lot of experience with certain languages which may cause them to be biased towards that language. Furthermore, Höst, Regnell and Whohlin \cite{host2000using} make the case that ``The reason to use students as subjects is often that they are available at universities
and they are willing to participate in studies as part of courses they attend.'' which is highly approprpiate given that we will be asking our peers and those in lower years who will eventually also be required to perform research tasks. The SEM program was chosen due to it being accessible for the researchers.

99 - 3rd year
168 - 2nd year
190 - 1st year

Overlap: 50 (Those who are in another group)
Total: 397

Population in the facebook groups.

count here - estimate desired response rate, error rate etc
Sampling bias is a considerable challenge in research \cite{easterbrook2008selecting}

\newline

@@

@@

\SubSection{Threats to Validity}
As in all research there are threats to the validty of the study being undertaken. Our largest threat would be the external validty of the data collected. The students were selected from the three current years studying at the University of Gothenburg. Most of the respondants indicated that they are in the first year of their studties and as such their inexperience could be a limiting factor on their answers to the survey. The students may also have had a bias for one of the languages; Java. So far, the students in the first year have been formally taught in only Java. This means that there is a lower chance they would be familiar with reading other language syntax other than java and as such they would be more likely to see Java favourably than others. We cannot therefore generalise that Java has higher readability than that of the other languages despite what the results show.

A further threat that we were unable to counteract adequately was the willing to participate of our respondants. The participants had little or no incentive to actually partake in the study and as such many most likely simply ingored it. This is to be expected when one attempts to undertakes a single stage sampling method. One idea to improve the response rate for further surveys could be to form some incentive for the respondants.

Threat - Open groups. No control over who is in them so potentially we can have respondants who are not knowledgeable answering questions.
